---
title: "NOAA Tagging Final Report"
author: "Adam A Kemberling"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    mathjax: null
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

#Packages
library(tidyverse)
library(here)
library(stargazer)
library(sf)
library(knitr)
library(rnaturalearth)
library(gridExtra)
library(circular)
library(magrittr)

#Path to dropbox data
db_path <- "/Users/akemberling/Dropbox/csap_studies/tagging_analyses/Data"

####  Data  ####
#These files have had the regions we are interested in added and have had bad tags removed
# See the tagging_region_assignment.R script for details
tagging <- read_csv(str_c(db_path, "/final_report_datasets", "/tags_clean_final.csv"), 
                    col_types = cols()) %>% rename_all(tolower)
both <- read_csv(str_c(db_path, "/final_report_datasets", "/tags_recaps_clean_final.csv"), 
                   col_types = cols()) %>% rename_all(tolower)

# Spatial Polygons
usa_poly <- ne_states("united states of america") %>% st_as_sf() %>% filter(region == "South")
mexico_poly <- ne_states("mexico") %>% st_as_sf()
```

# Gulf Scale


##  Gulf-Wide Tagging Effort

```{r totals tagged}
tagging <- tagging %>% 
  mutate(
    tag_state = factor(tag_state, 
                       levels = c("Texas", "Louisiana", "Mississippi", "Alabama", "Florida")),
    tag_state = fct_explicit_na(tag_state, na_level = "Deep Water Event"))

tagging %>% 
  group_by(tag_state, tag_region) %>% 
  summarise(`Number Tagged` = n()) %>% 
  kable(caption = "Summary of Overall Tagging Effort")


```


## Gulf-Wide Travel Summary


```{r recaptures summary}
both <- both %>% 
  mutate(tag_state = factor(tag_state, 
                            levels = c("Texas", "Louisiana", 
                                       "Mississippi", "Alabama", "Florida")))

both %>% 
  group_by(tag_state, tag_region) %>% 
  summarise(`Number Recaptured` = n(),
            `Average Time at Liberty (days)` = mean(time_at_large, na.rm = T),
            `Average Distance Travelled (km by water)` = mean(lc_distance / 1000),
            `Mean Travel Rate (km/day over water)` = mean((lc_distance/1000) / time_at_large)) %>% 
  ungroup() %>% rename(`Tagging State` = tag_state,
                       `Tagging Region` = tag_region) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  kable(caption = "Summary of Time at Liberty and Travel Rate for Recaptures by their Release State and Sub-region")
```


##  Gulf-Wide Tagging State and Recapture States/Regions


```{r}
both %>% 
  group_by(tag_state, tag_region) %>% 
  count(recap_state, recapture_region) %>%  
  rename("Tagging State" = tag_state,
         "Recapture State" = recap_state,
         "Recapture Region" = recapture_region,
         "Number of Crabs" = n) %>% 
  kable(caption = "Start and End States/Regions for Recaptured Crabs")
```

---  
---   

# State Scale

##   State-Scale Travel Summary

```{r}
both %>% 
  group_by(tag_state) %>% 
  summarise(`Number Recaptured` = n(),
            `Average Time at Liberty (days)` = mean(time_at_large, na.rm = T),
            `Average Distance Travelled (km by water)` = mean(lc_distance / 1000),
            `Mean Travel Rate (km/day over water)` = mean((lc_distance/1000) / time_at_large)) %>% 
  ungroup() %>% rename(`Tagging State` = tag_state) %>% 
  mutate_if(is.numeric, round, 2) %>%  
  kable(caption = "Summary of Time at Liberty and Travel Rate for Recaptures by their Release State")
```

##   State-Scale Tagging State and Recapture State

```{r}
both %>% 
  group_by(tag_state) %>% 
  count(recap_state) %>%  
  rename("Tagging State" = tag_state,
         "Recapture State" = recap_state,
         "Number of Crabs" = n) %>% 
  kable(caption = "Start and End States for Recaptured Crabs")
```

---
---

# Basin Scale

##   Basin-Scale Travel Summary

o   Total numbers tagged when (maybe a figure with calendar month and numbers tagged

o   Maps of tagging and recaptures

```{r}
both %>% 
  group_by(tag_region) %>% 
  summarise(`Number Recaptured` = n(),
            `Average Time at Liberty (days)` = mean(time_at_large, na.rm = T),
            `Average Distance Travelled (km by water)` = mean(lc_distance / 1000),
            `Mean Travel Rate (km/day over water)` = mean((lc_distance/1000) / time_at_large)) %>% 
  ungroup() %>% rename(`Tagging Region` = tag_region) %>% 
  mutate_if(is.numeric, round, 2) %>%  
  kable(caption = "Summary of Time at Liberty and Travel Rate for Recaptures by their Release Region")
```


##   Directions travelled (exclude crabs that travelled < 5km for this)

o   Rao’s test for each

```{r, message=FALSE, warning=FALSE}
hist(both$bearing)
hist(both$windrose_bearing)

#Circle Plots
region_circ <- both %>% 
  #Filter minimum distances out
  filter(lc_distance >= 5000) %>% 
  #Split by Region
  split(.$tag_region) %>% 
  #Pull the bearing info and make circular objects
  map(function(x) {
    bearings <- select(x, windrose_bearing)
    as.circular(bearings, 
                units = "degrees",
                zero = pi/2,
                rotation = "clock")
    
  })


#Make Plots so you can check orientation
region_circ %>% imap(function(.x, .y) {circular::plot.circular(.x, main = paste(.y))})


#Kernel Plots


region_circ %>% imap(function(.x, .y) {
  res_25 <- density.circular(.x, bw = 25)
  plot(res_25, points.plot = TRUE,
       shrink = 1.3,
       main = paste(.y), 
       #main = str_c(.y, "\nKernel Density Plot"), 
       ylab = "")
  
  })



#Rao's Test
#?circular::rao.test()

```


o   Crabs recaptured within home estuary

o   Crabs captured somewhere else

##  Travel rates (Maybe exclude crabs that have long times at liberty? Start with 1 month)

o   What patterns stand out: mean and variance etc. by season


---
---
 
# Crabs outside of Estuaries

##   Map of only Gulf Crabs




##   Any recaptures



