---
title: "Offshore Modeling - Manuscript Model"
author: "Adam A. Kemberling"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
  code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

#packages
library(multcomp)
library(ggspatial)
library(MASS)
library(here)
library(tidyverse)
library(knitr)
library(emmeans)
library(patchwork)
library(gridExtra)
library(broom)
library(statmod)
library(sf)

conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")


#Format ggplot for rest of document
theme_set(theme_bw() + 
          theme(
            panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(), 
            panel.border = element_rect(fill = NA),
            axis.text = element_text(size = 12, color = "black"),
            axis.title = element_text(size = 12, color = "black"),
            legend.text = element_text(size = 12, color = "black"),
            legend.background = element_rect(fill = NA),
            strip.text = element_text(size = 12, color = "black"))
          )

`%not in%` <- purrr::negate(`%in%`)
```

# Manuscript Model

```{r load data}
seamap <- read_csv(str_c("~/Dropbox/csap_studies/seamap_analyses/data/offshore/", 
                        "seamap_manuscriptmods_full.csv"), 
                   guess_max = 1e4,
                   col_types = cols()) %>% 
  mutate(year_f = factor(year_f),
         Season = factor(season, levels = c("Summer", "Fall")), #For tables
         season = factor(season, levels = c("Summer", "Fall")), #For models
         region = ifelse(region == "Louisiana", "LA West", region),
         region = factor(region, levels = c("Texas", "LA West", "MS Bight", "Florida"))
)

seamap_west <- read_csv(str_c("~/Dropbox/csap_studies/seamap_analyses/data/offshore/", 
                        "seamapwest_manuscriptmods_full.csv"), 
                        guess_max = 1e4,
                        col_types = cols()) %>% 
  mutate(year_f = factor(year_f),
         Season = factor(season, levels = c("Summer", "Fall")),
         season = factor(season, levels = c("Summer", "Fall")),
         region = ifelse(region == "Louisiana", "LA West", region),
         region = factor(region, levels = c("Texas", "LA West", "MS Bight", "Florida"))
)
```


## Model Dataset {.tabset}

### Model Data - West Only

```{r seamap west stats}
start_year    <- min(as.numeric(as.character(seamap_west$survey_year)))
end_year      <- max(as.numeric(as.character(seamap_west$survey_year)))
total_catch   <- sum(seamap_west$sapidus_catch, na.rm = T)
overall_foa   <- round(mean(seamap_west$crab_presence, na.rm = TRUE), 3) * 100
percent_zeros <- seamap_west %>% filter(sapidus_catch == 0) %>% count()
station_count <- seamap_west %>% count()
overall_mean  <- round(mean(seamap_west$cpue_towspd, na.rm = T), 3)
overall_se    <- round(sd(seamap_west$cpue_towspd, na.rm = T) / sqrt(station_count), 3)

seamap_west %>% 
  #group_by(region, statzone) %>% 
  group_by(region) %>% 
  summarise(n = n()) %>% 
  rename_all(str_to_title) %>% 
  kable()


# # Statzone tally check
# seamap_west %>% 
#   group_by(survey_year, season, statzone) %>% 
#   summarise(n_samples = n()) %>% 
#   ungroup() %>% 
#   mutate(header = str_c(survey_year, "_", season)) %>% 
#   select(-c(survey_year, season)) %>% 
#   pivot_wider(names_from = header, values_from = n_samples) %>% 
#   clipr::write_clip()
#   write.table(., "clipboard", sep="\t", row.names=FALSE)
```
   
 * Total Number of Stations = `r nrow(seamap_west)`     
 
 * Starting in `r start_year` and continuing through `r end_year`     
 
 * Total Sapidus Caught was `r total_catch`     
 
 * Overall Frequency of Occurrence was `r overall_foa`  

 * Overall Mean Catch Crabs/Hectare: `r overall_mean`   
 
 * Overall Standard Error `r overall_se`    
 
 * Stations with no catch: `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`%    
 
```{r seamap all stats, eval = FALSE}
### East + West


start_year    <- min(as.numeric(as.character(seamap$survey_year)))
end_year      <- max(as.numeric(as.character(seamap$survey_year)))
total_catch   <- sum(seamap$sapidus_catch, na.rm = T)
overall_foa   <- round(mean(seamap$crab_presence, na.rm = TRUE), 3) * 100
overall_mean  <- round(mean(seamap$cpue_towspd, na.rm = T), 3)
percent_zeros <- seamap %>% filter(sapidus_catch == 0) %>% count()
station_count <- seamap %>% count()
overall_se    <- round(sd(seamap$cpue_towspd, na.rm = T) / sqrt(station_count), 3)


seamap %>% 
  #group_by(region, statzone) %>% 
  group_by(region) %>% 
  summarise(n = n()) %>% 
  rename_all(str_to_title) %>% 
  kable()

# #checking salinity ranges
# library(magrittr)
# seamap %$% range(.$salinity_b, na.rm = T)
# seamap %$% hist(.$salinity_b)
# seamap %$% quantile(.$salinity_b, probs = c(0, 0.05, .5, 0.95, 1), na.rm = T)
# 
# seamap %>% filter(sapidus_catch > 0) %$% range(.$salinity_b, na.rm = T)
# seamap %>% filter(sapidus_catch > 0) %$% hist(.$salinity_b)
# seamap %>% filter(sapidus_catch > 0) %$% quantile(.$salinity_b, probs = c(0, 0.05, .5, 0.95, 1), na.rm = T)




   
 * Total Number of Stations = `r nrow(seamap)`     
 
 * Starting in `r start_year` and continuing through `r end_year`     
 
 * Total Sapidus Caught was `r total_catch`     
 
 * Overall Frequency of Occurrence was `r overall_foa`  

 * Overall Mean Catch Crabs/Hectare: `r overall_mean`      
 
 * Overall Standard Error `r overall_se`    
 
 * Stations with no catch: `r percent_zeros` / `r station_count` Stations **or** `r round((percent_zeros / station_count) * 100, 2)`% 

```
 
## Annual Catch and Occurrence {.tabset}

### Data Summary

*NOTE: Contains Data Only from Western-Gulf Subset*

```{r}
year_sums <- seamap_west %>% 
  group_by(survey_year) %>% 
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(cpue_towspd)),
            `Mean Catch`      = mean(cpue_towspd, na.rm = T),
            `SD`              = sd(cpue_towspd, na.rm = T),
            `Var`             = var(cpue_towspd),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`),
            `% Occurrence`    = mean(crab_presence, na.rm = T),
            `% Occurrence SE` = sd(crab_presence, na.rm = T) / sqrt(Stations - `Missing Obs`)
            ) %>% 
  ungroup() %>% 
    mutate(Survey_Year        = factor(survey_year),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin),
           occurrence_ymin    = `% Occurrence` - (2 * `% Occurrence SE`),
           occurrence_ymax    = `% Occurrence` + (2 * `% Occurrence SE`),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin)
         )


year_sums %>% 
  select(`Survey Year` = survey_year, Stations, `Missing Obs`, 
         `% Occurrence`, `Mean Catch`, SD, `Overdispersed`) %>% knitr::kable()
```

### Annual Mean Catch

```{r, fig.height = 4}

west_mean <- round(mean(seamap_west$cpue_towspd, na.rm = T), 3)

year_plot <- year_sums %>% 
  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
  ggplot() +
    geom_col(aes(survey_year, `Mean Catch`), fill = "gray50") +
    geom_errorbar(aes(x = survey_year, 
                      ymin = catch_ymin,
                      ymax = catch_ymax),
                  size = .25) +
  geom_hline(yintercept = west_mean, 
             linetype = "dashed") +
  labs(x = NULL,
       y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))
  )


year_plot
```

### Annual Frequency of Occurrence

```{r, fig.height = 4}
west_foa <- round(mean(seamap_west$crab_presence, na.rm = TRUE), 3)

year_foa <- year_sums %>% 
  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
  ggplot() +
    geom_col(aes(survey_year, `% Occurrence`), fill = "gray50") +
    geom_hline(yintercept = west_foa, 
               linetype = "dashed") +
    scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
    labs(x = NULL, y = "Percent occurrence")

year_foa
```

### Side x Side

```{r, fig.height = 4}

year_plot + year_foa

```


## Region - Season Interactions {.tabset}

*NOTE: Contains Data Only from Western-Gulf Subset*


*NOTE 2: Mean Catch (per hectare) calculated as the average crabs/hectare from each tow within a region-season grouping. Percent occurrence is calculated separately as the average annual percent occurrence for those same groups.*

### Factor Summary

```{r }

#Mean CPUE for the regions within each season
rs_summary <- seamap_west %>%
  filter(is.na(region)      == FALSE) %>%
  group_by(region, season) %>%
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(cpue_towspd)),
            `Mean Catch`      = mean(cpue_towspd, na.rm = T),
            `SD`              = sd(cpue_towspd, na.rm = T),
            `Var`             = var(cpue_towspd),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>%
    ungroup() %>%
    mutate(Season             = factor(season, levels = c("Summer", "Fall")),
           region             = factor(region,
                                       levels = c("Texas", "LA West", "MS Bight", "Florida")),
           #region             = fct_rev(region),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin)
    )


#Summary Table
rs_summary %>%
  select(Region = region, Season, Stations, `Missing Obs`, `Mean Catch`, SD, Overdispersed) %>%
  knitr::kable()





####  Full Gulf Summaries  ####
#Mean CPUE for the regions within each season
rs_summary_full <- seamap %>%
  filter(is.na(region)      == FALSE) %>%
  group_by(region, season) %>%
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(cpue_towspd)),
            `Mean Catch`      = mean(cpue_towspd, na.rm = T),
            `SD`              = sd(cpue_towspd, na.rm = T),
            `Var`             = var(cpue_towspd),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>%
    ungroup() %>%
    mutate(Season             = factor(season, levels = c("Summer", "Fall")),
           region             = factor(region,
                                       levels = c("Texas", "LA West", "MS Bight", "Florida")),
           #region             = fct_rev(region),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin)
    )
#Calaculate Annual average percent occurrence
rs_foa_full <- seamap %>% 
  group_by(survey_year, region, season) %>% 
  summarise(percent_occurrence = mean(crab_presence, na.rm = T)) %>% 
  group_by(region, season) %>% 
  summarise(nyears = n(),
            avg_percent_occurrence = mean(percent_occurrence, na.rm = T),
            po_se = sd(percent_occurrence, na.rm = T) / sqrt(nyears)) %>% 
    ungroup() %>%
    mutate(Season             = factor(season, levels = c("Summer", "Fall")),
           region             = factor(region, levels = c("Texas", "LA West", 
                                                          "MS Bight", "Florida")),
           occurrence_ymin    = avg_percent_occurrence - (2 * po_se),
           occurrence_ymax    = avg_percent_occurrence + (2 * po_se),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin),
           occurrence_ymax    = ifelse(occurrence_ymax > 1, 1, occurrence_ymax)
    )

```


Average frequency of occurrence for each region and season is calculated in two steps. In the first step the frequency of occurrence for each region and for both survey seasons is calculated for every year. In the second step those annual means are averaged to get an overall measure for each region for each season, and a measure of error around them is calculated to represent the inter-annual variation in the frequency of occurrence.

```{r west summs}



#Calaculate Annual average percent occurrence
rs_foa <- seamap_west %>% 
  group_by(survey_year, region, season) %>% 
  summarise(percent_occurrence = mean(crab_presence, na.rm = T)) %>% 
  group_by(region, season) %>% 
  summarise(nyears = n(),
            avg_percent_occurrence = mean(percent_occurrence, na.rm = T),
            po_se = sd(percent_occurrence, na.rm = T) / sqrt(nyears)) %>% 
    ungroup() %>%
    mutate(Season             = factor(season, levels = c("Summer", "Fall")),
           region             = factor(region, levels = c("Texas", "LA West", 
                                                          "MS Bight", "Florida")),
           occurrence_ymin    = avg_percent_occurrence - (2 * po_se),
           occurrence_ymax    = avg_percent_occurrence + (2 * po_se),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin),
           occurrence_ymax    = ifelse(occurrence_ymax > 1, 1, occurrence_ymax)
    )

rs_foa %>% 
  select(Region = region, Season, `N Years` = nyears, 
         `% Occurrence` = avg_percent_occurrence, `% Occurrence SE` = po_se) %>%
  knitr::kable()

```


### Mean Catch by Region and Season

```{r west fig, fig.height = 4, eval = F}

# # Plot
# rs_plot <- rs_summary %>% 
#   ggplot(aes(region, `Mean Catch`, fill = Season)) +
#     geom_col(position = "dodge") +
#     geom_errorbar(aes(ymin = catch_ymin,
#                       ymax = catch_ymax),
#                   position = "dodge", 
#                   size = .25) +
#   scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
#   labs(x = NULL,
#        y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) + 
#   theme(
#     legend.position = c(1, .95),
#     legend.justification = c("right", "top"),
#     legend.box.just = "right",
#     legend.margin = margin(0, 6, 2, 2))
# 
# 
# rs_plot
```


```{r full fig, fig.height = 4}

# Plot
rs_plot_3 <- rs_summary_full %>% 
  ggplot(aes(region, `Mean Catch`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = catch_ymin,
                      ymax = catch_ymax),
                  position = "dodge", 
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
  labs(x = NULL,
       y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = .8))


rs_plot_3
```

### Frequency of Occurrence

```{r west foa, fig.height = 4, eval = F}
# rs_plot_2 <- rs_foa %>% 
#   ggplot(aes(region, avg_percent_occurrence, fill = Season)) +
#     geom_col(position = "dodge") +
#     geom_errorbar(aes(ymin = occurrence_ymin,
#                       ymax = occurrence_ymax),
#                   position = "dodge",
#                   size = .25) +
#   scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
#   scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
#   labs(x = NULL,
#        y = "Percent occurrence") + 
#   theme(
#     legend.position = c(1, .95),
#     legend.justification = c("right", "top"),
#     legend.box.just = "right",
#     legend.margin = margin(0, 6, 2, 2))
# 
# rs_plot_2
```



```{r full foa, fig.height = 4}
rs_plot_4 <- rs_foa_full %>% 
  ggplot(aes(region, avg_percent_occurrence, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = NULL,
       y = "Percent occurrence") + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = .8))

rs_plot_4
```

### Side x Side

```{r fig.height = 4, eval = FALSE}
# rs_plot <- rs_plot + theme(legend.position = "none")
# rs_plot + rs_plot_2
```


```{r fig.height = 4}

rs_plot_full <- rs_plot_3 + theme(legend.position = "none")
rs_plot_full + rs_plot_4
```








## Candidate Models {.tabset}

### Model Selection using AIC

```{r}

#Candidate 1 - no interactions
candidate_1 <- MASS:::glm.nb(
  sapidus_catch ~ year_f + region + season +   #Additive covariates
  offset(log(area_hectares)),
  data = seamap_west)

#Candidate 2 - year * region
candidate_2 <- MASS:::glm.nb(
  sapidus_catch ~ year_f + region + season +   #Additive covariates
  year_f * region + 
  offset(log(area_hectares)),
  data = seamap_west)

#Candidate 3 - year * season
candidate_3 <- MASS:::glm.nb(
  sapidus_catch ~ year_f + region + season +   #Additive covariates
  year_f * season + 
  offset(log(area_hectares)),
  data = seamap_west)

#Candidate 4 - region * season
candidate_4 <- MASS:::glm.nb(
  sapidus_catch ~ year_f + region + season +   #Additive covariates
  region * season + 
  offset(log(area_hectares)),
  data = seamap_west)

#Candidate 5 - year * region + region * season
candidate_5 <- MASS:::glm.nb(
  sapidus_catch ~ year_f + region + season +   #Additive covariates
  year_f * region + region * season +
  offset(log(area_hectares)),
  data = seamap_west)

#Candidate 6 - All interactions
candidate_6 <- MASS:::glm.nb(
  sapidus_catch ~ year_f * region * season + 
  offset(log(area_hectares)),
  data = seamap_west)

model_list <- list(
  "no interactions"               = candidate_1,
  "year * region"                 = candidate_2,
  "year * season"                 = candidate_3,
  "region * season"               = candidate_4,
  "Year * region & year * season" = candidate_5,
  "all interactions"              = candidate_6
)

model_aic <- map(model_list,AIC)
model_aic <- bind_rows(
  imap(model_aic, function(x,y) {
    aic_df <- data.frame("Formulation" = y, AIC = x) }
    )
  )
model_aic %>% mutate(`Delta AIC` = AIC - min(AIC)) %>% knitr::kable()

best_mod <- candidate_6
rm(candidate_1, candidate_2, candidate_3, candidate_4, candidate_5, candidate_6)


# # Check number of predictions from model vs. number of positive catch
# # To determine whether 0 catch is dropped or not
# predict(best_mod, type = "response") %>% length()
# seamap_west %>% filter(sapidus_catch > 0) %>% nrow()
# 
# #How many predictions are exactly 0
# sum(predict(best_mod, type = "response") == 0)
```

### Predictor Significance


```{r}

#Drop1 method
#drop1(mod1a, test = "F")     # F-test
#drop1(mod1a, test = "Chisq") # Chisq LRT - no scope

#Name what you want to drop
lrt_y  <- drop1(best_mod, scope = ~ year_f, test = "Chisq")
lrt_r  <- drop1(best_mod, scope = ~ region, test = "Chisq")
lrt_s  <- drop1(best_mod, scope = ~ season, test = "Chisq")
lrt_yr <- drop1(best_mod, scope = ~ year_f * region, test = "Chisq")

#Dropping year * season for global model
lrt_ys <- drop1(best_mod, scope = ~ year_f * season, test = "Chisq")

#Dropping region * season for global
lrt_rs <- drop1(best_mod, scope = ~ region * season, test = "Chisq")

bind_rows(
  list(
    lrt_y  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor"),
    lrt_r  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region"),
    lrt_s  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor") %>% filter(Predictor == "season"),
    lrt_yr  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor") %>% filter(Predictor == "year_f:region"),
    lrt_ys  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor") %>% filter(Predictor == "year_f:season"),
    lrt_rs  %>% as.data.frame() %>% 
      rownames_to_column(var = "Predictor") %>% filter(Predictor == "region:season")
    
)) %>% kable()



#broom::glance(best_mod) %>% kable()
#Percent deviance explained
perc_dev <- (best_mod$null.deviance - best_mod$deviance) / best_mod$null.deviance
perc_dev <- round(perc_dev * 100,2)
```

*Percent Deviance Explained by Best Candidate Model:* `r perc_dev`


### Model Summary

Statistic reported below is the Wald Chi-Square z-score.

```{r}
#summary(best_mod) #to see what test statistic is used
broom::tidy(best_mod) %>% kable()
```


### Interaction Plots

```{r}
emmip(best_mod, 
      region ~ year_f, type = "response", offset = 0) + 
  labs(x = NULL, caption = "Interaction Plot for year * region factors") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5),
        legend.position = c(0.8, 0.8))
```

```{r}
emmip(best_mod, 
      season ~ region, type = "response", offset = 0) + 
  labs(x = NULL, caption = "Interaction Plot for region * season factors") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5),
        legend.position = c(0.8, 0.8))
```

```{r}
emmip(best_mod, 
      season ~ year_f, type = "response", offset = 0) + 
  labs(x = NULL, caption = "Interaction Plot for year * season factors") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5),
        legend.position = c(0.8, 0.8))
```


###  Tukey HSD multiple comparison test {.tabset .tabset-pills}


####  Test 1. Region

```{r}
summary(glht(best_mod, mcp(region = "Tukey")))
```

####  Test 2. Year

```{r}
summary(glht(best_mod, mcp(season = "Tukey")))
```

## Catch per Hectare Plot {.tabset .tabset-pills}

### Seasonal Prediction Differences

```{r}

#Estimated Marginal Means with an offset
#parameter in the call of offset = 0:
best_mod_dat <- as.data.frame(emmeans(best_mod, 
                                  specs = "year_f", 
                                  by    = c("region", "season"),
                                  type  = "response", 
                                  offset = 0))
best_mod_dat$CV <- best_mod_dat$SE/best_mod_dat$response

#Drop Infinite credibility intervals
best_mod_dat <- best_mod_dat %>% 
  mutate(asymp.UCL = ifelse(asymp.UCL == Inf, NA, asymp.UCL),
         season = factor(season, levels = c("Summer", "Fall")),
         region = factor(region, levels = c("Texas", "LA West", "MS Bight")))


# Catch Plot
p <- best_mod_dat %>% 
  mutate(year_n = as.numeric(as.character(year_f))) %>% 
  ggplot(aes(year_n, response)) +
      geom_line(aes(year_n, response, color = season)) +
      geom_point(aes(year_n, response, color = season, shape = season)) +
      scale_color_grey(start = 0.35, end = 0.7) + 
      labs(
        x = NULL, 
        y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) +
      facet_grid(region ~ .) +
  theme(
    legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    legend.title = element_blank())
p

```

### Observed vs. Predicted Data {.tabset}

```{r}
#Observed data
mean_obs <- mean(seamap_west$cpue_towspd)
obs_timeline <- seamap_west %>% 
  group_by(survey_year, region, season) %>% 
  summarise(Nobs = n(),
            PercentPos = mean(crab_presence),
            Mean_CPUE = mean(cpue_towspd)) %>% 
  ungroup() %>% 
  mutate(season = factor(season, levels = c("Summer", "Fall")),
         region = factor(region, levels = c("Texas", "LA West", "MS Bight")),
         Index_Obs = Mean_CPUE/mean_obs)



#Overall group means
panel_means <- seamap_west %>% 
  group_by(region, season) %>% 
  summarise(Mean_CPUE = mean(cpue_towspd)) %>% 
  ungroup() %>% 
  mutate(season = factor(season, levels = c("Summer", "Fall")),
         region = factor(region, levels = c("Texas", "LA West", "MS Bight")))


```

#### Original

```{r}
# Model predictions and observed means
p <- best_mod_dat %>% 
  mutate(year_n = as.numeric(as.character(year_f))) %>% 
  ggplot(aes(year_n, response)) +
    geom_ribbon(aes(year_n,
                    ymin = asymp.LCL,
                    ymax = asymp.UCL),
                fill = "gray80") +
    geom_line(aes(x = year_n, 
                  y = response, 
                  group = 1, 
                  col = "Predicted")) +
    geom_point(aes(x = year_n, 
                   y = response, 
                   col = "Predicted")) +
    # Observed Data
    geom_line(data = obs_timeline, 
            aes(x = survey_year, 
                y = Mean_CPUE, 
                group = region, 
                col = "Observed"), linetype = 2) +
    geom_point(data = obs_timeline, 
               aes(x = survey_year, 
                   y = Mean_CPUE, 
                   group = region, 
                   col = "Observed")) +
    #Group Means
    # geom_hline(data = panel_means, 
    #            aes(yintercept = Mean_CPUE), alpha = 0.5, linetype = 1, color = "darkred") +
    #Theme changes
    #scale_color_grey(start = 0.35, end = 0.7) + 
    scale_color_manual(values = c("royalblue", "black")) + 
    labs(
      x = NULL, 
      y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) +
  theme(legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    legend.title = element_blank()) +
  facet_grid(season~region)
p

```

#### Predictions Only


```{r}
# Model Predictions Only
p <- best_mod_dat %>% 
  mutate(year_n = as.numeric(as.character(year_f))) %>% 
  ggplot(aes(year_n, response)) +
    geom_ribbon(aes(year_n,
                    ymin = asymp.LCL,
                    ymax = asymp.UCL),
                fill = "gray80") +
    geom_line(aes(x = year_n, 
                  y = response, 
                  group = 1), 
                  col = "black") +
    geom_point(aes(x = year_n, 
                   y = response), 
                   col = "black") +
    # # Group Means
    # geom_hline(data = panel_means,
    #            aes(yintercept = Mean_CPUE,
    #                color = "Group Mean"), 
    #            size = 1,
    #            alpha = 0.5, 
    #            linetype = 2) +
    # scale_color_manual(values = c("darkred")) + 
    # Theme changes
    labs(
      x = NULL, 
      y = expression(paste(" Predicted Mean CPUE (crabs ", ha^{-1},")"))) +
  theme(legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    legend.title = element_blank()) +
  facet_grid(season~region)
p
```

####  Observed Only

```{r}
# Observed Means Only
p <- ggplot(
      data = obs_timeline, 
      aes(x = survey_year, 
          y = Mean_CPUE)) +
    geom_line(
      aes(group = region), 
      col = "black", 
      linetype = 1) +
    geom_point(
      aes(group = region), 
      col = "black") +
    labs(
      x = NULL, 
      y = expression(paste("Observed Mean CPUE (crabs ", ha^{-1},")"))) +
  theme(legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    legend.title = element_blank()) +
  facet_grid(season~region)
p
```


## Raster Plots  {.tabset}

*NOTE: Contains Data Only from Western-Gulf Subset*

```{r spatial data setup}

library(stars)
library(sf)
library(rnaturalearth)

#State and Country Bounds
usmap <- ne_states(country = "united states of america") %>% 
  st_as_sf() %>% 
  filter(region == "South")

mex <- ne_states(country = "mexico") %>% 
  st_as_sf()

## Statistical Zones


#Load the simplified nmfs grid
szones <- read_sf("~/Dropbox/csap_studies/seamap_analyses/data/gis_files/nmfs_grids_clipped_rough.shp", 
                  crs = 4326) #%>% st_simplify()







####  Custom grids for rasterize  ####

test_bbox <- st_bbox(c(xmin = -97.5, xmax = -81,
                       ymin = 24.3, ymax = 30.5),
                     crs = st_crs(4326))

num_x <- seq(from = -97.4, to = -81.3, by = 0.2)
num_y <- seq(from = 24.4, to = 30.4, by = 0.2)



####  Aggregation  ####

season_rasters <- seamap_west %>% 
  mutate(lon_bin = round(start_long, 1),
         lat_bin = round(start_lat, 1)) %>% 
  split(.$season) %>% 
  map(function(x) {
  
    #Aggregating the seamap data into bins
    seamap_sf_agg <- x %>% 
      group_by(lon_bin, lat_bin) %>% 
      summarise(n_stations = n(),
                total_catch = sum(sapidus_catch, na.rm = T),
                avg_cpue = mean(cpue_towspd),
                cpue_variance = sd(cpue_towspd, na.rm = T) ^ 2) %>% 
      st_as_sf(coords = c("lon_bin", "lat_bin"), crs = 4326, remove = FALSE)

    ####  Total Catch  ####
    
    #Convert to Raster and plot 
    catch_ras <- st_rasterize(
      seamap_sf_agg["total_catch"],
      template = st_as_stars(
          test_bbox,
          #st_bbox(seamap_sf), 
          values = NA_real_,
          nx = length(num_x),
          ny = length(num_y))
      )
    
    
    ####  Mean CPUE  ####
    
    cpue_ras <- st_rasterize(
      seamap_sf_agg["avg_cpue"],
      template = st_as_stars(
          test_bbox,
          #st_bbox(seamap_sf), 
          values = NA_real_,
          nx = length(num_x),
          ny = length(num_y))
      )
    
    
    #### CPUE Vaiance ####
    
    variance_ras <- st_rasterize(
      seamap_sf_agg["cpue_variance"],
      template = st_as_stars(
          test_bbox,
          #st_bbox(seamap_sf), 
          values = NA_real_,
          nx = length(num_x),
          ny = length(num_y))
      )
    
    
    ####  Sampling Effort  ####
    effort_ras <- st_rasterize(
      seamap_sf_agg["n_stations"],
      template = st_as_stars(
          test_bbox,
          #st_bbox(seamap_sf), 
          values = NA_real_,
          nx = length(num_x),
          ny = length(num_y))
      )
    
    
    ####  Output List  ####
    return(list(
      "agg_data" = seamap_sf_agg, # In case we need to use geom_tile
      "catch" = catch_ras,
      "effort" = effort_ras,
      "variance" = variance_ras,
      "cpue" = cpue_ras
    ))

})

```


### Statistical Zones
```{r}

#Numbering for statzones
sz_df <- tribble(
~"SZ", ~"long",  ~"lat",
21,    -96.5,     26.5,
20,    -96.7,  27.5,
19,    -95.75,  28.25,
18,    -94.5,   28.8,
17,    -93.5,   28.9,
16,    -92.5,   28.85,
15,    -91.5,   28.8,
14,    -90.5,   28.75,
13,    -89.75,  28.9,
12,    -89.25,  29.65,
11,    -88.5,   29.75,
10,    -87.5,   29.80,
 9,    -86.5,   29.80,
 8,    -85.5,   29.35,
 7,    -84.20,   29.45,
 6,    -83.8,   28.50,
 5,    -83.5,   27.55,
 4,    -83.35,   26.75,
 3,    -83.35,   25.75,
 2,    -84.20,   24.55,
 2,    -81.55,   24.28,
 1,    -82.5,   24.28

) %>% mutate(SZ = as.character(SZ))

west_zones <- c(21:13, 11)


# # Entire Gulf
# ggplot() +
#   geom_sf(data = szones, fill = NA) + # Full Gulf
#   geom_sf(data = usmap) +
#   geom_sf(data = mex) +
#   geom_text(data = sz_df, aes(long, lat, label = SZ), size = 3.5) + # Full
#   coord_sf(xlim = c(-98, -81), ylim = c(24, 31), datum = NA) + # Full
#   labs(x = NULL, y = NULL)  +
#   scale_y_continuous(breaks = c(25,30)) +
#   annotation_north_arrow(
#     height = unit(0.4, "in"),
#     location = "bl",
#     which_north = "true",
#     pad_x = unit(0, "in"),
#     pad_y = unit(0, "in"),
#     style = north_arrow_fancy_orienteering) +
#   annotation_scale(pad_x = unit(0.5, "in"))


# West Only
ggplot() +
  geom_sf(data = filter(szones, StatZone %in% west_zones), fill = NA) + # West
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  geom_text(data = filter(sz_df, SZ %in% west_zones), 
            aes(long, lat, label = SZ), size = 3.5) + # West
  coord_sf(xlim = c(-98, -87.95), ylim = c(25.75, 31), datum = NA) + # West
  labs(x = NULL, y = NULL)  +
  scale_y_continuous(breaks = c(25,30)) #+
  # annotation_north_arrow(
  #   height = unit(0.4, "in"),
  #   location = "bl", 
  #   which_north = "true", 
  #   pad_x = unit(4.15, "in"), 
  #   pad_y = unit(0, "in"),
  #   style = north_arrow_fancy_orienteering) +
  # annotation_scale(pad_x = unit(2.8, "in")) # West
```




### Sampling Effort

```{r}

####  Entire Gulf  ####

# ####  Sampling Effort  ####
# ggplot() +
#   geom_stars(data = effort_ras) +
#   geom_sf(data = usmap) +
#   geom_sf(data = mex) +
#   scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
#   coord_sf(xlim = c(-98, -81), ylim = c(24, 31), datum = NA) +
#   scale_y_continuous(breaks = c(25,30)) +
#   labs(x = NULL, y = NULL) +
#   guides(fill = guide_colorbar(title = "Total Sampling Effort (Stations)",
#                                title.hjust = 0.5, 
#                                title.position = "top",
#                                barwidth = 10)) +
#   theme(legend.position = "bottom", 
#         legend.text = element_text(size  = 12), 
#         legend.title = element_text(size = 12)) +
#   annotation_north_arrow(
#     height = unit(0.4, "in"),
#     location = "bl", 
#     which_north = "true", 
#     pad_x = unit(0, "in"), 
#     pad_y = unit(0, "in"),
#     style = north_arrow_fancy_orienteering) +
#   annotation_scale(
#     pad_x = unit(0.5, "in"))




####  West Only  ####

# Summer
ggplot() +
  geom_stars(data = season_rasters$Summer$effort) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -87.95), ylim = c(25.75, 31), datum = NA) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Total Sampling Effort (Stations)",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(5.85, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(pad_x = unit(4.25, "in")) # West


# Fall

ggplot() +
  geom_stars(data = season_rasters$Fall$effort) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -87.95), ylim = c(25.75, 31), datum = NA) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Total Sampling Effort (Stations)",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(5.85, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(pad_x = unit(4.25, "in")) # West
```

### Catch per Hectare

```{r}

####  CPUE  ####

# ####  Entire Gulf  ####
# ggplot() +
#   geom_stars(data = cpue_ras) +
#   geom_sf(data = usmap) +
#   geom_sf(data = mex) +
#   scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
#   coord_sf(xlim = c(-98, -81), ylim = c(24, 31), datum = NA) +
#   scale_y_continuous(breaks = c(25,30)) +
#   labs(x = NULL, y = NULL) +
#   guides(fill = guide_colorbar(title = "Average Catch/Hectare",
#                                title.hjust = 0.5, 
#                                title.position = "top",
#                                barwidth = 10)) +
#   theme(legend.position = "bottom", 
#         legend.text = element_text(size  = 12), 
#         legend.title = element_text(size = 12)) +
#   annotation_north_arrow(
#     height = unit(0.4, "in"),
#     location = "bl", 
#     which_north = "true", 
#     pad_x = unit(0, "in"), 
#     pad_y = unit(0, "in"),
#     style = north_arrow_fancy_orienteering) +
#   annotation_scale(
#     pad_x = unit(0.5, "in"))

# Summer
ggplot() +
  geom_stars(data = season_rasters$Summer$cpue) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -87.95), ylim = c(25.75, 31), datum = NA) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Average Catch/Hectare",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(5.85, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(pad_x = unit(4.25, "in")) # West

# Fall
ggplot() +
  geom_stars(data = season_rasters$Fall$cpue) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -87.95), ylim = c(25.75, 31), datum = NA) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Average Catch/Hectare",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(5.85, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(pad_x = unit(4.25, "in")) # West

```


### Variance in CPUE

```{r}
####  Catch Variance  ####

####  Entire Gulf  ####
# ggplot() +
#   geom_stars(data = variance_ras) +
#   geom_sf(data = usmap) +
#   geom_sf(data = mex) +
#   scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
#   coord_sf(xlim = c(-98, -81), ylim = c(24, 31), datum = NA) +
#   scale_y_continuous() +
#   labs(x = NULL, y = NULL) +
#   guides(fill = guide_colorbar(title = "Variance in Average Catch/Hectare",
#                                title.hjust = 0.5, 
#                                title.position = "top",
#                                barwidth = 10)) +
#   theme(legend.position = "bottom", 
#         legend.text = element_text(size  = 12), 
#         legend.title = element_text(size = 12)) +
#   annotation_north_arrow(
#     height = unit(0.4, "in"),
#     location = "bl", 
#     which_north = "true", 
#     pad_x = unit(0, "in"), 
#     pad_y = unit(0, "in"),
#     style = north_arrow_fancy_orienteering) +
#   annotation_scale(
#     pad_x = unit(0.5, "in"))


# Summer
ggplot() +
  geom_stars(data = season_rasters$Summer$variance) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -87.95), ylim = c(25.75, 31), datum = NA) +
  scale_y_continuous() +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Variance in Average Catch/Hectare",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(5.85, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(pad_x = unit(4.25, "in")) # West


# Fall
ggplot() +
  geom_stars(data = season_rasters$Fall$variance) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -87.95), ylim = c(25.75, 31), datum = NA) +
  scale_y_continuous() +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Variance in Average Catch/Hectare",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(5.85, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(pad_x = unit(4.25, "in")) # West
```




### Total Catch

```{r}
####  Total Catch  ####


####  Entire Gulf  ####
# ggplot() +
#   geom_stars(data = catch_ras) +
#   geom_sf(data = usmap) +
#   geom_sf(data = mex) +
#   scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
#   coord_sf(xlim = c(-98, -81), ylim = c(24, 31), datum = NA) +
#   scale_y_continuous(breaks = c(25,30)) +
#   labs(x = NULL, y = NULL) +
#   guides(fill = guide_colorbar(title = "Total C. sapidus Caught",
#                                title.hjust = 0.5, 
#                                title.position = "top",
#                                barwidth = 10)) +
#   theme(legend.position = "bottom", 
#         legend.text = element_text(size  = 12), 
#         legend.title = element_text(size = 12)) +
#   annotation_north_arrow(
#     height = unit(0.4, "in"),
#     location = "bl", 
#     which_north = "true", 
#     pad_x = unit(0, "in"), 
#     pad_y = unit(0, "in"),
#     style = north_arrow_fancy_orienteering) +
#   annotation_scale(
#     pad_x = unit(0.5, "in"))

# Summer
ggplot() +
  geom_stars(data = season_rasters$Summer$catch) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -87.95), ylim = c(25.75, 31), datum = NA) +
  scale_y_continuous() +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Variance in Average Catch/Hectare",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(5.85, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(pad_x = unit(4.25, "in")) # West

# Fall
ggplot() +
  geom_stars(data = season_rasters$Fall$catch) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -87.95), ylim = c(25.75, 31), datum = NA) +
  scale_y_continuous() +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Variance in Average Catch/Hectare",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(5.85, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(pad_x = unit(4.25, "in")) # West
```


### Outlining Cells with Geom_Tile

```{r}
# Fall
ggplot() +
  geom_tile(data = season_rasters$Summer$agg_data, 
            aes(x = lon_bin, y = lat_bin, fill = n_stations), 
            color = "white", size = 0.05) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -87.95), ylim = c(25.75, 31), datum = NA) +
  scale_y_continuous() +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Total Stations - Summer",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(5.85, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(pad_x = unit(4.25, "in")) # West
```




### Study Area Size From Convex Hull

```{r}
# #summer stations only
# summer_sf <- seamap_west %>% 
#   filter(season == "Summer") %>% 
#   st_as_sf(coords = c("start_long", "start_lat"), crs = 4326, remove = FALSE)
# 
# 
# #make convex hull from multipoints object
# summer_hull <- st_convex_hull(st_union(summer_sf))
# 
# # Intersect with the statzones we care about
# important_zones <- szones %>% dplyr::filter(StatZone %in% seamap_west$statzone)
# summer_hull_t <- st_intersection(summer_hull, important_zones)
# summer_hull_sf <- st_as_sf(summer_hull_t)
# 
# #plot it out
# ggplot() +
#   geom_sf(data = usmap) +
#   geom_sf(data = mex) +
#   geom_sf(data = summer_hull_sf, color = "royalblue", fill = NA) +
#   coord_sf(xlim = c(-98, -81), ylim = c(24, 31), datum = NA)
# 
# 
# #Gebco bathymetric data
# bathy <- raster::raster("/Users/adamkemberling/Dropbox/csap_studies/seamap_analyses/data/gis_files/GEBCO/gebco_2019.tif")
# 
# #60 fathom bathymetry as sp object
# bathy60 <- raster::rasterToContour(bathy, levels = c(-60 * 1.8288))
# bathy60_sf <- st_as_sf(bathy60, crs = 4326)
# 
# 
# # Trim polygon using raster
# # OR clip raster and select cells < 60fm then create new polygon
# bathy_mask <- raster::mask(bathy, mask = summer_hull_sf)
# bathy_crop <- raster::crop(bathy_mask, y = summer_hull_sf)
# 
# # Now create a depth mask for < 60fm
# bathy_test <- bathy_crop
# bathy_test[bathy_crop < (-60 * 1.8288)] <- NA
# plot(bathy_test, main = "Depths <= 60 fathoms")
# 
# 
# ####  Get area from raster  ####\#get sizes of all cells in raster [km2]
# cell_size <- raster::area(bathy_test, na.rm=TRUE, weights=FALSE)
# 
# #delete NAs from vector of all raster cells
# ##NAs lie outside of the rastered region, can thus be omitted
# cell_size <- cell_size[!is.na(cell_size)]
# 
# #compute area [km2] of all cells in geo_raster
# raster_area <- length(cell_size) * median(cell_size)
# raster_area <- round(raster_area, digits = 1)

# Pre-processing determined raster area to be
raster_area <- 122297.8 #square kilometers

# Print area of Study Area according to raster object
print(paste("Area of Analysis Data Study Area (raster):", raster_area,"km2"))

print(paste("Area of Analysis Data Study Area (raster):", raster_area * 100, "Hectares"))


# If we want to use the polygon area instead, should use an equal area projection
# proj string details here:
# https://proj.org/operations/projections/laea.html 

```

